---
title: "Status Internet Argument Data Set"
fontsize: 10pt
header-includes:
- \usepackage{booktabs}
output: 
  beamer_presentation:
      theme: Madrid
      colortheme: beaver
---

```{r setup, include=FALSE}
library(data.table)
library(xtable)
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.align="center", fig.ext="pdf")
s_input <- "./data/output/tables.RData"
load(s_input)

dtToLatexTable <- function(dt_table, s_file = "",  
                           s_caption = NULL, 
                           s_label = NULL, 
                           s_align = NULL, 
                           v_i_digits = NULL,
                           s_size = NULL){
  
  x_dt_table <- xtable(dt_table,
                       align = s_align,
                       caption = s_caption,
                       digits = v_i_digits,
                       label = s_label)
  print(x_dt_table,  
        file = s_file,
        table.placement="H",
        size = s_size,
        include.rownames = FALSE,
        comment = FALSE,
        booktabs = TRUE
  )
  
}

```

## Goal


Create a data set based on Internet Argument Corpus data which includes 

* original post 

* response 

* topic

* mechanical turk annotations

link to source: [https://nlds.soe.ucsc.edu/iac2](https://nlds.soe.ucsc.edu/iac2)

## Current status

Data set with 

* original post 

* response 

* topic

* 1 out of 3 mechanical turk data incorporated

See files:  

* script: script/extractCombineTables.R 

* output: ./data/output/quoteResponseMTurk.RData

## Observations

Summary count:

```{r results='asis'}
dtToLatexTable(l_tables[["dt_summary"]],s_size = "tiny")
```

* Only a small sample of post-responses have been labeled by Mechanical Turk
    - 10K vs 540K  Based on 1 out of 3 Mechanical turk data 

## Proposed next steps

* Include other 2 mechanical turk data sources

* Create response variable that only has text which responds to original post
    - had problems creating this variable due to encoding
